---
title: '`r paste0("Personalised Endoscopy Report for Evaluation and Continuous Training (PERFECT) for ",params$EndoscopistChooserIn,format(Sys.time(), " %d %B, %Y"))`'
always_allow_html: yes
output:
  word_document:
    fig_caption: true
    reference_docx: !expr here::here("word-styles-reference-01.docx")

params:
  EndoscopistChooserIn: NA
  Map_EndoscopistIn: NA
  ProceduresDone: NA
  BarrEQPerformFinalTable: NA
  EndoscopyTypesDonePre: NA
  performanceTable: NA
  IndicsVsBiopsiesPre: NA
  GRS_perEndoscopist_TablePrep: NA
  polypLocationLowerGI: NA
---

Please find enclosed a breakdown of results from your endoscopic assessments. The results are organised. At the end of the report there are metrics which you can compare your performance to.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir=here::here())

library(ggplot2)
library(xtable)
library(ggpubr)
library(kableExtra)

```

\newpage
***
# Table of endoscopy and histology
***
\
\

# Cancer Diagnoses Table


```{r cancerTable,warning=FALSE,echo=FALSE,warning=FALSE}

df<-params$performanceTable
df[,1]<-Hmisc::capitalize(as.character(df[,1]))
df[,2]<-Hmisc::capitalize(as.character(df[,2]))
df[,3]<-Hmisc::capitalize(as.character(df[,3]))

#Need to split the sentence up so can do negative remove on each sentence.
#Capitalise each sentence by simple gsubbing or recognition of a full stop (need to improve for bullet points though)
standardisedTextOutput<-str_split(df[,3], "\\.")
standardisedTextOutput<-lapply(standardisedTextOutput, function(x) NegativeRemove(x))
#Then need to recombine into one text:

df$NoNegatives<-sapply(standardisedTextOutput, function(x) paste(x,collapse="."))
#df$NoNegatives
    df<-df%>%filter(grepl("adenocar|malign|cancer|carcinoma",NoNegatives))


if(!is.null(df$Image)){
df$Image<-gsub("<img src=\'","",df$Image)
df$Image<-gsub("'>","",df$Image)
df$Image<-gsub("%20"," ",df$Image)
df$Image<-gsub("!\\[\\]\\(",paste0("!\\[\\]\\(",here::here(),"/www/"),df$Image)
df[,params$EndoscopistChooserIn]<-NULL
names(df)<-c("Endoscopist","Findings","Histology","Postive Diagnoses only","Images")

#Try to neaten up the Histology read-out:

Histology<-gsub("^\\.\\s+","")

names(df) <- pandoc.strong.return(names(df))
pander(df[,1:5],justify = c('left'),split.table = Inf)
} else {
  df[,1]<-Hmisc::capitalize(as.character(df[,1]))
df[,2]<-Hmisc::capitalize(as.character(df[,2]))
df[,3]<-Hmisc::capitalize(as.character(df[,3]))
  df[,params$EndoscopistChooserIn]<-NULL

  names(df)<-c("Hospital No.","Findings","Histology","Postive Diagnoses only")
  names(df) <- pandoc.strong.return(names(df))
pander(df[,1:4],justify = c('left'),split.table = Inf)

}


```


<br>
<br>
<br>

# Dysplasia Table

<br>
<br>
<br>

```{r dysplasiaTable,warning=FALSE,echo=FALSE,warning=FALSE}

df<-params$performanceTable
df[,1]<-Hmisc::capitalize(as.character(df[,1]))
df[,2]<-Hmisc::capitalize(as.character(df[,2]))
df[,3]<-Hmisc::capitalize(as.character(df[,3]))

#Need to split the sentence up so can do negative remove on each sentence.
#Capitalise each sentence by simple gsubbing or recognition of a full stop (need to improve for bullet points though)
standardisedTextOutput<-str_split(df[,3], "\\.")
standardisedTextOutput<-lapply(standardisedTextOutput, function(x) NegativeRemove(x))
#Then need to recombine into one text:

df$NoNegatives<-sapply(standardisedTextOutput, function(x) paste(x,collapse="."))
#df$NoNegatives
    df<-df%>%filter(grepl("dysplasia",NoNegatives))


if(!is.null(df$Image)){
df$Image<-gsub("<img src=\'","",df$Image)
df$Image<-gsub("'>","",df$Image)
df$Image<-gsub("%20"," ",df$Image)
df$Image<-gsub("!\\[\\]\\(",paste0("!\\[\\]\\(",here::here(),"/www/"),df$Image)
df[,params$EndoscopistChooserIn]<-NULL
names(df)<-c("Endoscopist","Findings","Histology","Postive Diagnoses only","Images")

#Try to neaten up the Histology read-out:

Histology<-gsub("^\\.\\s+","")

names(df) <- pandoc.strong.return(names(df))
pander(df[,1:5],justify = c('left'),split.table = Inf)
} else {
  df[,1]<-Hmisc::capitalize(as.character(df[,1]))
df[,2]<-Hmisc::capitalize(as.character(df[,2]))
df[,3]<-Hmisc::capitalize(as.character(df[,3]))
  df[,params$EndoscopistChooserIn]<-NULL

  names(df)<-c("Hospital No.","Findings","Histology","Postive Diagnoses only")
  names(df) <- pandoc.strong.return(names(df))
pander(df[,1:4],justify = c('left'),split.table = Inf)
}
    
```

<br>
<br>
<br>

# All Diagnoses Table

<br>
<br>
<br>

```{r EverythingTable,warning=FALSE,echo=FALSE,warning=FALSE}
df<-params$performanceTable
df[,1]<-Hmisc::capitalize(as.character(df[,1]))
df[,2]<-Hmisc::capitalize(as.character(df[,2]))
df[,3]<-Hmisc::capitalize(as.character(df[,3]))

#Need to split the sentence up so can do negative remove on each sentence.
#Capitalise each sentence by simple gsubbing or recognition of a full stop (need to improve for bullet points though)
standardisedTextOutput<-str_split(df[,3], "\\.")
standardisedTextOutput<-lapply(standardisedTextOutput, function(x) NegativeRemove(x))
#Then need to recombine into one text:

df$NoNegatives<-sapply(standardisedTextOutput, function(x) paste(x,collapse="."))
#df$NoNegatives
    df<-df%>%filter(!grepl("adenocar|malign|cancer|dysplasia",NoNegatives))


if(!is.null(df$Image)){
df$Image<-gsub("<img src=\'","",df$Image)
df$Image<-gsub("'>","",df$Image)
df$Image<-gsub("%20"," ",df$Image)
df$Image<-gsub("!\\[\\]\\(",paste0("!\\[\\]\\(",here::here(),"/www/"),df$Image)
df[,params$EndoscopistChooserIn]<-NULL
names(df)<-c("Endoscopist","Findings","Histology","Postive Diagnoses only","Images")

#Try to neaten up the Histology read-out:

Histology<-gsub("^\\.\\s+","")

names(df) <- pandoc.strong.return(names(df))
pander(df[,1:5],justify = c('left'),split.table = Inf)
} else {
  df[,1]<-Hmisc::capitalize(as.character(df[,1]))
df[,2]<-Hmisc::capitalize(as.character(df[,2]))
df[,3]<-Hmisc::capitalize(as.character(df[,3]))
  df[,params$EndoscopistChooserIn]<-NULL

  names(df)<-c("Hospital No.","Findings","Histology","Postive Diagnoses only")
  names(df) <- pandoc.strong.return(names(df))
pander(df[,1:4],justify = c('left'),split.table = Inf)
}
    
```
\newpage
***
# Barretts metrics- Grade detection and documentation of key elements on reports
***

```{r figsBarrettsHistopath, echo=FALSE, warning=FALSE,fig.width=7,fig.height=4,fig.align="center"}

if(nrow(params$EndoscopyTypesDonePre)>0){
key <- params$Map_EndoscopistIn
    if(!is.null(params$EndoscopistChooserIn)){
        if(length(params$EndoscopyTypesDonePre)>0){
          p1<-gghistogram(params$EndoscopyTypesDonePre,title="Barrett's Histopathological Grade", x = "IMorNoIM",fill = params$Map_EndoscopistIn, stat="count",font.xtickslab = c(14, "bold", "#2E9FDF"),font.ytickslab = c(14, "bold", "#2E9FDF"))+
            guides(fill=FALSE)+
            theme(axis.title.x=element_blank())+
            theme(legend.position = "right")+
            theme(plot.title = element_text(hjust = 0.5))+
   theme(axis.title.y = element_text(color = "grey20", size = 16, angle = 90, hjust = .5, vjust = .5, face = "plain"))+
                    theme(axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain")) 
           
        }
    }






      if(!is.null(params$EndoscopistChooserIn)){
         mydf<-params$BarrEQPerformFinalTable %>% filter(get(params$Map_EndoscopistIn) == params$EndoscopistChooserIn)
         p2<-gghistogram(mydf, title="Barrett's documentation",x = key, y = "PercentDocs", fill = "DocumentedElement", stat = "identity",position="dodge",font.font.ytickslab = c(14, "bold", "#2E9FDF"))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
        theme(legend.position = "bottom")+
           theme(legend.title = element_blank())+
           theme(plot.title = element_text(hjust = 0.5))+
   theme(axis.title.y = element_text(color = "grey20", size = 16, angle = 90, hjust = .5, vjust = .5, face = "plain"))+
                    theme(axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"))+
            labs(y="% Reports")
      }


ggarrange(p1,p2,ncol = 1, nrow = 2)

}
```

```{r ExpectedNumberBarrettsBx, echo=FALSE, warning=FALSE,fig.width=7,fig.height=4,fig.align="center"}

BarrettsCases<-params$EndoscopyTypesDonePre
if(!is.null(BarrettsCases$NumBx)){
  if(!is.null(BarrettsCases$CStage)){
ExpectedNumber <-BarrettsCases %>% summarise(MeanDiff = (sum(NumBx,na.rm=TRUE)-((mean(CStage,na.rm=TRUE)+1)*2)))
  }
}
```



#   `r ifelse(is.numeric(ExpectedNumber$MeanDiff),paste0("On average you took ",text_spec(ExpectedNumber$MeanDiff, color = "red")," biopsies versus the expected number of biopsies you should have taken for your Barrett's cases."),"")`


#   `r ifelse(min(mydf$PercentDocs<80),paste0("Some of your documentation for Barrett's was <80%. Documenting Barrett's anatomy helps in deciding follow-up timings for Barrett's patients. "),"")`

## [BSG Barrett's Guidelines here](https://www.bsg.org.uk/wp-content/uploads/2019/12/BSG-guidelines-on-the-diagnosis-and-management-of-Barretts-oesophagus.pdf?x19508),





\newpage
***
# Procedures performed
***

```{r figs_Proc, echo=FALSE, warning=FALSE,fig.width=8,fig.height=4,fig.align="center"}
if(nrow(params$ProceduresDone)>0){

#Get the number of procedures performed tabulated for the histogram:
MyProcedures<-params$ProceduresDone
MyProcedures$Var1<-as.character(MyProcedures$Var1)
MyProcedures$Var1<-stringr::str_wrap(MyProcedures$Var1,50)


 
 
   ggdotchart(MyProcedures, x = "Var1", y = "Freq",
           palette = c("#00AFBB", "#E7B800", "#FC4E07"), # Custom color palette
           sorting = "descending",                       # Sort value in descending order
           add = "segments",                             # Add segments from y = 0 to dots
           rotate = TRUE,                                # Rotate vertically
           dot.size = 10,                                 # Large dot size
           label = round(MyProcedures$Freq),                        # Add mpg values as dot labels

           ggtheme = theme_pubr(),                        # ggplot2 theme
                      font.label = list(color = "white", size = 8, 
                             vjust = 0.5)               # Adjust label parameters
           )
                      

}

```

\newpage
***
# Biopsies taken per indication- Your biopsies versus the average number of biopsies taken for that indication
***

```{r figs_Indic, echo=FALSE, warning=FALSE,fig.width=9,fig.height=4,fig.align="center"}

if(nrow(params$IndicsVsBiopsiesPre)>0){
myIndics<-params$IndicsVsBiopsiesPre
myIndics$Indications<-stringr::str_wrap(myIndics$Indications,50)
Mydata<-tidyr::gather(myIndics,"key","biopsyNumber",all_Mean:endoscopist_Mean)
ggdotchart(Mydata, x = "Indications", y = "biopsyNumber",
           group="key",color="key",
           palette = c("#00AFBB", "#E7B800", "#FC4E07"), # Custom color palette
           sorting = "descending",                       # Sort value in descending order
           add = "segments",                             # Add segments from y = 0 to dots
           rotate = TRUE,                                # Rotate vertically
           dot.size = 10,                                 # Large dot size
           label = round(Mydata$biopsyNumber),                        # Add mpg values as dot labels

           ggtheme = theme_pubr(),                        # ggplot2 theme
                      font.label = list(color = "white", size = 8, 
                             vjust = 0.5)               # Adjust label parameters
           )+
   labs(y="Number of biopsies")+
 labs(x="Indications")
}



```


\newpage
***
# Adenoma detection and subtypes- Your adenoma detection rate broken down by histopathological subtype
***

```{r figsPolpys, echo=FALSE,warning=FALSE, fig.width=7,fig.height=4,fig.align="center"}
if(nrow(params$GRS_perEndoscopist_TablePrep)>0){
MyPolypTable<-tidyr::gather(params$GRS_perEndoscopist_TablePrep,key="DocumentedElement",value="percentage",-!!rlang::sym(params$Map_EndoscopistIn))
p4<-gghistogram(MyPolypTable, title="",x = "DocumentedElement", y = "percentage", stat = "identity",position="dodge",fill="black")+
  theme(axis.title.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text.x=element_text(angle=45, hjust=1,size = 8))+
   theme(axis.title.y = element_text(color = "grey20", size = 16, angle = 90, hjust = .5, vjust = .5, face = "plain"))+
                    theme(axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"))



p4
}
```


#   `r ifelse(min(MyPolypTable$percentage[1]<15),paste0("Your adenoma detection rate is <15%. There may be several reasons for this. Are you detecting enough right sided polyps (see table below). "),"")`

```{r figsPolpysLocation, echo=FALSE,warning=FALSE, fig.width=7,fig.height=4,fig.align="center"}
if(nrow(params$polypLocationLowerGI)>0){
myPolypsLocation<-params$polypLocationLowerGI


p3<-gghistogram(myPolypsLocation, title="",x = "lowerGIPolyps", y = "Freq", stat = "identity",position="dodge",fill="black")+
  theme(axis.title.x=element_blank(),
        axis.ticks.x=element_blank())+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text.x=element_text(angle=45, hjust=1,size = 8))+
   theme(axis.title.y = element_text(color = "grey20", size = 16, angle = 90, hjust = .5, vjust = .5, face = "plain"))+
                    theme(axis.text.y = element_text(color = "grey20", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"))

p3
}

```